HealpixNet: Efficient spherical Convolutional Neural Networks with Healpix sampling for cosmological applications

### 2018-05-28 scnn.tex
todo
added new todos

\section{TODO list}
\begin{itemize}
    \item Michael, do you agree with the title HealpixNet
    \item
\end{itemize}

@@

>>>>

\section{TODO list}
\begin{itemize}
    \item Michael, do you agree with the title HealpixNet
    \item Emphaise the novelty of using it on Helapix in abstract, into and rest of the paper
    \item Finish section on Convolutions on graphs
    \item Plot of filters from Mass maps
    \item check the power spectrum after smoothing
    \item upgrade the plot of pooling
    \item new plot for network structure (teaser plot)
    \item add info on comparison with histogram, so that it's just a demonstration
    \item Figure 1 to be round
    \item finish section on Efficient convolutions
    \item conclusions
    \item (done!) results
    \item Results figure, add sigma8
    \item possibly move the eigen decomposition and heat into appendix + add discussion
\end{itemize}

@@

\citep{patton2017cosmologicalconstraints}
